\documentclass[journal]{IEEEtran}
% \usepackage{booktabs} % For formal tables
% \usepackage{times}
% \renewcommand{\rmdefault}{ptm}
\usepackage{multirow}
% \usepackage{array}
\usepackage{amsmath}
\usepackage{subfigure}
% \usepackage{bm}
% \usepackage{amsfonts}
\usepackage{epsfig}
\usepackage{psfrag}
% \usepackage{epstopdf}
%\usepackage{cite}
%\usepackage{url}
\newcounter{numberlistc}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{subfigure}
\usepackage{color}
\usepackage{spverbatim}
\usepackage{setspace}
\usepackage{caption}
%\usepackage{subcaption}

\newenvironment{numberlist}
    {   \setcounter{numberlistc}{0}
        \begin{list}{\arabic{numberlistc}.}
        {\usecounter{numberlistc}
        \setlength{\parsep}{0pt}
        \setlength{\topsep}{3pt}
        \setlength{\itemsep}{0pt}}
        }{ \end{list} }
\newcounter{itemlistc}
\newcounter{enumlistc}
%\renewcommand{\theromanlistc}{(\roman{romanlistc})} %for ref use
%\renewcommand{\thealphlistc}{(\alph{alphlistc})}    %for ref use
\newenvironment{itemlist}
    {   \setcounter{itemlistc}{0}
    \begin{list}{$\bullet$}
        {\usecounter{itemlistc}
        \setlength{\parsep}{0pt}
        \setlength{\topsep}{3pt}
        \setlength{\itemsep}{0pt}}
        }{ \end{list} } 

\newcommand{\rev}[1]{\textcolor{red}{#1}}

\renewcommand{\baselinestretch}{1}

% \newenvironment{packedenum}{
% \begin{enumerate}
% \setlength{\itemsep}{1pt}
% \setlength{\parskip}{0pt}
% \setlength{\parsep}{0pt}
% }{\end{enumerate}}

%\usepackage{setspace}
%\DeclareMathOperator{\rank}{rank}


%\renewcommand{\baselinestretch}{0.895}
%\IEEEoverridecommandlockouts
%\usepackage[font=small, labelfont=bf]{caption}
%\usepackage{caption}


%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\renewcommand{\algorithmiccomment}[1]{~~~~\textcolor{BrickRed}{// \textit{#1}}}


\begin{document}
\title{ EM-Aware Power Grid IR Drop Fixing Accelerated by Variational AutoEncoder}

%\author{\indent Yibo Liu~\IEEEmembership{Student Member,~IEEE}, 
%Sheldon X.-D. Tan~\IEEEmembership{Senior Member,~IEEE} 
%~\thanks{\indent Yibo Liu, and Sheldon X.-D. Tan are with the Department of Electrical and 
%Computer Engineering, University of California, Riverside, Riverside, CA 92521, USA~(e-mail: stan@ece.ucr.edu).}}


\maketitle
  
\begin{abstract}
Electromigration (EM) remains the top failure mechanism for copper-interconnected deep sub-micro technologies. 
This paper presents a Variational AutoEncoder (VAE)-based EM-aware IR drop prediction model for the full-chip power grid network.
Compared to the recently proposed generative adversarial network (GAN)-based method, our VAE model has a higher accuracy in terms of 40$\%$ RMSE reduction in mV.
We further extend our VAE-based fast EM-aware IR drop prediction model to a fast full-chip power grid IR-drop fixing framework.
We formulate the power grid EM-IR drop fixing as a optimization problem and solve it with sequence of linear programming (SLP) method, 
Ehe optimization is accelerated by the fast acquired aging-aware IR drop as the VAE model prediction output, and the sensitivity of aging-induced voltage to the initial PGN tree conductance from the model auto gradient. 
We show that the proposed VAE-accelerated EM-aware fixing method can lead up to 90X (at least one order of magnitude) speedup over the conventional SLP-based method on synthesized power grid benchmarks from ARM Cortex-M0 processor design.



\end{abstract}
 
\input intro.tex

\input related.tex

\input strategy.tex

\input results.tex

\section{Conclusion}
\label{sec:conclusion}
In this paper, we proposed a VAE accelerated power grid
fixing method based on a recently proposed linear programming based
optimization framework.  But instead of using the numerical matrix
solving method for obtaining the sensitivity information, which is
computationally slow and does not scale well for more violations, we
proposed to use the VAE-based model to accelerate sensitivity
computation.  Numerical results on a number of synthesized power grid
benchmarks from ARM Cortex-M0 processor designs show that the proposed
method can lead to at least one order of magnitude speedup over the
existing SLP based method. 




% \clearpage 
\bibliographystyle{IEEEtran}
\bibliography{../../bib/simulation,../../bib/modeling,../../bib/reduction,../../bib/misc,../../bib/mscad_pub,../../bib/reliability,../../bib/interconnect,../../bib/thermal_power,../../bib/machine_learning,../../bib/physical,../../bib/neural_network}
%\bibliography{bibfile}
%\input change_note.tex
% \input {bio.tex}

\end{document}
